The problem and promise of scale in multilayer networks

### 2020-01-22 paper/manuscript.Rmd
quick describe spatial buffer
quick describe default thresholds
quick describe metrics

@@

1. spatial threshold
1. number of observations
1. time window length
1. time window position

@@

>>>>

Unless otherwise mentioned, the spatial threshold is 50 and the temporal threshold is 5 minutes.

@@

Each modal landcover, and the original are sampled and separate network layers constructed for each.

1. spatial threshold

Social networks constructed using spatsoc. Multilayer networks constructed for each season. Variable modified is the spatial buffer. Series from 5 to 500.

1. number of observations

Randomly select max number of observations - timegroups -  (right now 750). For each iteration, include n observations for each season for all individuals. Subsequent iterations include nstep more (right now 25), along with previously included to remove stochasticity. Parallels with observation data.

1. time window length

Varying length of time window (used to define seasons). From 75 to 150 right now. Fixed start julian day for winter is day 1 and for summer is 215. Network layers for winter and summer are calculated for each window length.

1. time window position
Varying position of time window (used to define seasons). Fixed length at 75. Window positions starting at 1, to + 75. So 1-75 is first iteration for winter and 75-150 is second iteration for "winter". Same for summer, starting at 215. Network layers for each season are constructed.

@@

Right now, we calculate mostly degree/neighborhood based metrics.

* Degree centrality
* Multidegree
* Degree deviation: standard deviation of degree across layers

* Neighbors/neighborhood (number of unique actors directly connected to each focal)

Neighbors = degree within a network layer
But across a multilayer network with multiple layers, some neighbors are repeated.

So the difference between neighbors and degree is the basis for

* Connective redundancy: 1 - (neighborhood / degree) When connective redundancy is 0, all edges on all layers are necessary to preserve the social ties

* Relevance: neighborhood of specific layer  / neighbourhood of full ml net. This is the proportion of neighbors present on the layer of focus. Comparing across, it tells you which layers are most important for each individual.

Then there will be some layer similarity. Right now it's just a correlation of each season's asnipe SRI matrix

Finally, some weighted variable.
